Effective Inclusion of Electronic Polarization to a Negatively Charged Membrane

### 2018-09-26 Manuscript/manuscript.tex
Improved density-profile figure with PC:PS mixed membranes and added NaCl/KCl concentrations.

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/density_profile_K-Na_counterions_compar_pure-ECC-POPS.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged POPS bilayers using ECC-lipids and ECC-ions.  }
\todo{Joe: this figure requires updating and polishing, but serves the purpose of “showing the data”.}
\end{figure}

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/density_profiles_na_k_cl_wat_phos_models-compar_4-6_NaCl-and-KCl-series.pdf}
  \caption{\label{fig:nacl-dens_PCPS} 
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} and \ce{Cl^-} along the membrane normal axis 
    for the negatively charged membranes with the composition of 5\,PC:1\,PS using ECC-lipids and ECC-ions.  
    The top profile shows the simulation without any additional salt concentration, i.e., only with \ce{Na^+} counterions. 
    The middle profile shows the simulation with an additional \ce{KCl} concentration and \ce{Na^+} counterions. 
    The bottom profile shows the simulation with an additional \ce{NaCl} concentration and \ce{Na^+} counterions, which are not distinguished from the added salt. 
    In order to visualize the density profiles with a scale comparable to the profile of \ce{Ca^{2+}}, 
    the density profiles of~\ce{Cl^-}, \ce{K^+} and \ce{Na^+} ions are divided by 2, and 
    the density profiles of phosphate groups and water are divided by 5 and 200, respectively.  
  }
  \todo{SAMULI: Top figure should go together with figure of only K+ counterions and figure with pure PS mentioned
    another todo point
  } \\
  \todo{SAMULI: Division of ion densities with 2 in figure without calcium is not necessary and makes
  comparison to other results more difficult.}
\end{figure}

>>>>

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/density_profile_K-Na_counterions_compar_pure-ECC-POPS.pdf}
  \caption{\label{fig:POPS-counterions-dens}
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} counterions along the membrane normal axis 
    for the negatively charged POPS bilayers using ECC-lipids and ECC-ions.  }
\todo{Joe: TO BE UPDATED + results from PC:PS mixutres to be added.}
\end{figure}

\begin{figure}[tbp!] 
  \centering 
  \includegraphics[width=\figwidth]{../img/ecc_pops/density_profiles_na_k_cl_wat_phos_models-compar_5-6_NaCl-and-KCl-series.pdf}
  \caption{\label{fig:nacl-dens_PCPS} 
    Number density profiles of \ce{K^{+}}, \ce{Na^{+}} and \ce{Cl^-} along the membrane normal axis 
    for the negatively charged membranes with the composition of 5\,PC:1\,PS using ECC-lipids and ECC-ions
    from simulations with added concentrations of \ce{KCl} or \ce{NaCl}.  
    The top    profile shows the simulation with an additional \ce{KCl} concentration and \ce{Na^+} counterions. 
    The bottom profile shows the simulation with an additional \ce{NaCl} concentration and \ce{Na^+} counterions, which are not distinguished from the added salt. 
    The density profiles of phosphate groups and water are divided by 4 and 100, respectively.  
  }
\end{figure}
